---
title: "Map with leaflet"
author: "David Taylor"
date: "9/23/2021"
output: html_document
---

# Merchant location for the CU Boulder Faltiron Meal Plan

## 1. Synopsis
This assignment consists of creating a map with the locations of merchants included in the CU Boulder flatironmeal plan (https://flatironmealplan.com/). The merchant addresses were used to retrieve longitude and latitudes via gpsvisualizer and stored as "flatironmeals_merchants_lng_lat.csv". The "flatironmeals_merchants_lng_lat.csv" file will be used as starting point for this assignment. These merchants are broken down into 5 groups  (On campus, Convenient store, Gas station, Grocery store, Restaurants) and each group will have it's own colored marker on the map.

## 2. Houskeeping
```{r setup, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaflet)
```


## 3. Load merchant data
```{r import_data}
#flatironmeals_merchants_lng_lat.csv in working directory
df <- read.csv(paste0(getwd(), "/flatironmeals_merchants_lng_lat.csv"))
```
## 4. Generate map
```{r mmap_data}

icons <- awesomeIcons(
  icon = "fa-bullseye",
  iconColor = 'black',
  library = 'fa',
  markerColor = df$merchant_type_color2)
  
df %>% 
  leaflet() %>%
  addTiles() %>%
  #addMarkers(popup = df$name)
addAwesomeMarkers(lng = ~lng, lat = ~lat, icon = icons,label = ~as.character(name))%>%
addLegend(labels = c("On campus", "Convenience store", "Gas station", "Grocery store", "Restaurant"), 
                     colors = c("orange","red","pink","green", "#56B4E9"), opacity = 0.75)


```